Forecasting the old age dependency ratio to determine the best pension age

### 2019-01-05 PensionAge.Rmd
MBSportrait.pdf

---
title: "Forecasting the old age dependency ratio to determine the best pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Monash University
- familyname: Shang
  othernames: Hanlin
  address: Australian National University
abstract: "We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population. We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%. This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "blah, blah"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    includes:
      in_header: preamble.tex
---

@@

The issue is not only a problem for the government, but also for future retirees. Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65). They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}. This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR03].

@@

In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
\begin{equation}
  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \E[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
\end{equation}
where $\hat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process. For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process as follows:
\begin{equation}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2,\dots,J,
\end{equation}
where the parameters are estimated using maximum likelihood estimation.

@@

The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align*}
  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
\end{align*}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge. Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19). From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

@@

Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age. Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation}
  \bm{p}_{n+1}=[p_{mi}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation}
When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}.
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix (22). The simulations of total number of work age become a vector:
\begin{equation}
  \bm{p}^{work}_{n+1} = [\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
  \bm{p}^{aged}_{n+1}=[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]
\end{equation}

@@

# HMD credentials
username <- "rob.hyndman@buseco.monash.edu.au"
password <- "Q234.,mnb"

# Get population data for 1 Jan 2015
auspop <- hmd.pop("AUS", username, password, "Australia")
auspop <- extract.ages(auspop, age = 0:100)

@@

##### MIGRATION
aus.mig <- netmigration(aus.mort, aus.fert, startyearpop = auspop, mfratio = 1.05)
```

@@

ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2019-01-04)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mortf, fertf, migf, firstyearpop = auspop, N = nsim)
```

@@

```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
######## Run a rolling forecast origin
t <- 2010 - 1950 + 1
H <- 25 ## forecast horizon for test
k <- 25 ## years of data required to make a forecast
oadrtest <- matrix(0, 25, t - k - H)
for (i in 1:(t - k - H))
{
  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
  pop.short <- extract.years(auspop, years = 1949 + i + (0:k))
  mort.fit.s <- coherentfdm(ausmort.short)
  mortfs <- forecast(mort.fit.s, H)
  fert.fit.s <- fdm(ausfert.short)
  # Fix problem
  #  miss <- is.na(fert.fit.s$residuals$y)
  #  fert.fit.s$residuals$y[miss] <- 0
  # End fix
  fertfs <- forecast(fert.fit.s, H)
  mig.fit.s <- coherentfdm(ausmig.short)
  migfs <- forecast(mig.fit.s, H)
  aus.sim.s <- pop.sim(mortfs, fertfs, migfs, firstyearpop = pop.short, N = 3)
  oadp.fs <- oadr(pop.short, aus.sim.s)
  oadrtest[, i] <- oadp.fs$mean
}
oadrtest
oadr.real <- oadr(auspop, aus.sim)$x
oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
for (i in 1:25)
  oadr.real.mat[i, ] <- oadr.real[(i + 59):(59 + 11 + i)]

>>>>

---
title: "Forecasting the old age dependency ratio to determine the best pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Monash University
- familyname: Shang
  othernames: Han Lin
  address: Australian National University
abstract: "We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population. We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%. This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "functional time series model, coherent forecasts, demographic components, pension and insurance"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    includes:
      in_header: preamble.tex
---

@@

The issue is not only a problem for the government, but also for future retirees. Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65). They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}. This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR02].

@@

In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
\begin{equation}
  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \text{E}[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
\end{equation}
where $\hat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process. For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process as follows:
\begin{equation}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2,\dots,J,
\end{equation}
where the parameters are estimated using maximum likelihood estimation.

@@

The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align*}
  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
\end{align*}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge. Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19). From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

@@

Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age. Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation}
  \bm{p}_{n+1}=[p_{mi}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation}
When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}.
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix (22). The simulations of total number of work age become a vector:
\begin{equation}
  \bm{p}^{work}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
  \bm{p}^{aged}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]
\end{equation}

@@

# HMD credentials
username <- "shl8858@telstra.com"
password <- "hshang85"

hmd.pop <- function (country, username, password, label = country) 
{
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Population.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(pop) == "try-error") 
        stop("Population file not found at www.mortality.org")
    obj <- list(type = "population", label = label, lambda = 0)
    obj$year = sort(unique(pop[, 1]))
    n <- length(obj$year)
    m <- length(unique(pop[, 2]))
    obj$age <- pop[1:m, 2]
    mnames <- names(pop)[-c(1, 2)]
    n.pop <- length(mnames)
    obj$pop <- list()
    for (i in 1:n.pop) {
        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
        dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
    }
    names(obj$pop) <- tolower(mnames)
    obj$age <- as.numeric(as.character(obj$age))
    if (is.na(obj$age[m])) 
        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
    return(structure(obj, class = "demogdata"))
}

hmd.mx <- function (country, username, password, label = country) 
{
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Mx_1x1.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    mx <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(mx) == "try-error") 
        stop("Connection error at www.mortality.org. Please check username, password and country label.")
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Exposures_1x1.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(pop) == "try-error") 
        stop("Exposures file not found at www.mortality.org")
    obj <- list(type = "mortality", label = label, lambda = 0)
    obj$year <- sort(unique(mx[, 1]))
    n <- length(obj$year)
    m <- length(unique(mx[, 2]))
    obj$age <- mx[1:m, 2]
    mnames <- names(mx)[-c(1, 2)]
    n.mort <- length(mnames)
    obj$rate <- obj$pop <- list()
    for (i in 1:n.mort) {
        obj$rate[[i]] <- matrix(mx[, i + 2], nrow = m, ncol = n)
        obj$rate[[i]][obj$rate[[i]] < 0] <- NA
        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
        dimnames(obj$rate[[i]]) <- dimnames(obj$pop[[i]]) <- list(obj$age, 
            obj$year)
    }
    names(obj$pop) = names(obj$rate) <- tolower(mnames)
    obj$age <- as.numeric(as.character(obj$age))
    if (is.na(obj$age[m])) 
        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
    return(structure(obj, class = "demogdata"))
}

# Get population data for 1 Jan 2015
auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
auspop <- extract.ages(auspop, age = 0:100)

@@

aus.fert_v0 = extract.years(aus.fert, 1921:2014)

##### MIGRATION
aus.mig <- netmigration(mort = aus.mort, fert = aus.fert_v0, mfratio = 1.05)
```

@@

ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
ausfert.sm <- smooth.demogdata(aus.fert_v0, obs.var = "theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2019-01-04)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
```

@@

```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
######## Run a rolling forecast origin
t <- 2010 - 1950 + 1
H <- 25 ## forecast horizon for test
k <- 25 ## years of data required to make a forecast
oadrtest <- matrix(0, 25, t - k - H)
for (i in 1:(t - k - H))
{
  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
  pop.short <- extract.years(auspop, years = 1949 + i + (0:k))
  mort.fit.s <- coherentfdm(ausmort.short)
  mortfs <- forecast(mort.fit.s, H)
  fert.fit.s <- fdm(ausfert.short)
  # Fix problem
  #  miss <- is.na(fert.fit.s$residuals$y)
  #  fert.fit.s$residuals$y[miss] <- 0
  # End fix
  fertfs <- forecast(fert.fit.s, H)
  mig.fit.s <- coherentfdm(ausmig.short)
  migfs <- forecast(mig.fit.s, H)
  aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs, firstyearpop = pop.short, 
                       N = 3)
  oadp.fs <- oadr(pop.short, aus.sim.s)
  oadrtest[, i] <- oadp.fs$mean
}
oadrtest
oadr.real <- oadr(auspop, aus.sim)$x
oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
for (i in 1:25)
  oadr.real.mat[i, ] <- oadr.real[(i + 59):(59 + 11 + i)]
